Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-05-09 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
updates to intro

	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release. Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating. In the case of high-frequency heating, $\langle t_N\rangle$, the time between successive events, is such that $\langle t_N\rangle\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $\langle t_N\rangle\gg\tau_{cool}$ \citep{cargill_modelling_2015}. Steady heating is just high-frequency heating in the limit $\langle t_N\rangle\to0$. \hl{Discuss past heating frequency studies}

@@

	\par Hydrodynamic models of nanoflare-heated loops have found similar results when calculating emission measure slopes. While \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$. \citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<\langle t_N\rangle<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the observed emission measure slopes be found. This is consistent with the findings of \citet{ugarte-urra_determining_2014} who estimated an inter-event period of 1400 s using an event detection algorithm on filtered SDO/AIA 94 \ang images of AR cores. \hl{Steady-heating counter arguments?}

@@

	\par\hl{Hot slope calculations, predictions} A similar scaling has been claimed for hot emission such that $\mathrm{EM}\propto T^{-b}$. Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $T_m\lesssim\log{T}\lesssim7.2$. However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012}, using spectral measurements from EIS, provided hotward fits for $\mathrm{EM}$ reconstructions for a large number of ARs. All measured slopes fell in the range $6.1<b<10.3$, with large uncertainties on each hotward fit. \hl{more refs here? Summarize in a sentence or two and provide many refs, don't want to repeat paper 1}

@@

	\par \citet{cargill_implications_1994,cargill_nanoflare_2004} have predicted that emission measure distributions resulting from nanoflare models should be wide and have a faint, high-temperature (8-10 MK) component and thus a steep hotward slope, the so-called ``smoking gun'' of nanoflare heating. Unfortunately, observing this high-temperature emission is difficult and in some cases impossible. The reason for this difficulty is twofold. First, thermal conduction is a very efficient cooling mechanism at high temperatures and large spatial temperature gradients. When a loop is heated impulsively, its temperature rises quickly while the increase in density lags behind. By the time the density has increased sufficiently (due to chromospheric evaporation brought about by the response of the transition region to the strong downward coronal heat flux) to allow for an appreciable amount of emission (recalling $\mathrm{EM}\propto n^2$), thermal conduction has cooled the loop far below its initial hot temperature, making a direct detection of $\sim10$ MK plasma very difficult.

>>>>

	\par \citet{cargill_implications_1994,cargill_nanoflare_2004} have predicted that emission measure distributions resulting from nanoflare models should be wide and have a faint, high-temperature (8-10 MK) component, the so-called ``smoking gun'' of nanoflare heating. Though many workers \citep{reale_evidence_2009,schmelz_hinode_2009,miceli_x-ray_2012,testa_hinode/eis_2012,del_zanna_elemental_2014,petralia_thermal_2014,schmelz_hot_2015} have claimed evidence of this hot, faint component of the emission measure, poor spectral resolution \citep{testa_temperature_2011,winebarger_defining_2012} and non-equilibrium ionization \citep{bradshaw_explosive_2006,reale_nonequilibrium_2008} have made a positive detection of nanoflare heating difficult. However, \citet{brosius_pervasive_2014}, using obsservations from the \textit{EUNIS-13} sounding rocket, identified relatively faint emission from Fe XIX in a non-flaring active region (AR), suggesting temperatures of $\sim8.9$ MK.

@@

	\par A similar scaling has been claimed for hot emission such that $\mathrm{EM}\propto T^{-b}$. Typically, this power-law fit to the emission measure is done ``hotward'' of the peak, usually in the range $T_m\lesssim\log{T}\lesssim7.2$. However, measured values of these hotward slopes are poorly constrained due to both the magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012}, find $7\lesssim b\lesssim10$, with uncertainties of $\pm2.5-3$, for 15 AR cores thoguh \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$.

@@

	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release. Nanoflare heating is often classified as either \textit{high-frequency} or \textit{low-frequency} heating. In the case of high-frequency heating, $\langle t_N\rangle$, the time between successive events, is such that $\langle t_N\rangle\ll\tau_{cool}$, where $\tau_{cool}$ is the loop cooling time, and in the case of low-frequency heating $\langle t_N\rangle\gg\tau_{cool}$ \citep{cargill_modelling_2015}. Steady heating is just high-frequency heating in the limit $\langle t_N\rangle\to0$. \hl{Why heating frequency difficult? Need for modeling.}

@@

	\par Hydrodynamic models of nanoflare-heated loops have found similar results when calculating emission measure slopes. While \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$. \citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<\langle t_N\rangle<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found. This is consistent with the findings of \citet{ugarte-urra_determining_2014} who estimated an inter-event period of 1400 s from filtered SDO/AIA \citep{pesnell_solar_2012,lemen_atmospheric_2012} 94 \ang images of AR cores using an event detection algorithm. \hl{Steady-heating counter arguments?}
	\par\hl{Heating frequency and emssion $T>T_m$}
